### 2015-01-16 src/analysis.Rnw
update

\begin{figure*}
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
bcol <- '#2171B5'
icol <- '#9ECAE0'
m.db <- subset(allmutants.db, total > 0)
d.db <- subset(allmutants.db, detected > 0)
m.db$mutations <- m.db$mtotal * 100.0 / m.db$total
d.db$detected <- d.db$mdetected * 100.0 / d.db$detected

@@

#grid.newpage()
#pushViewport(viewport(layout = grid.layout(1, 2)))
#print(p1, vp = vplayout(1, 1))
#print(p2, vp = vplayout(1, 2))

@
\caption{The relative contribution of mutation operators in terms of fraction of mutants produced and detected. The produced mutants are shown with black outline while detected mutants have blue border and shade.}
\end{figure*}

>>>>

\begin{figure*}
<<mutantdet,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
bcol <- '#2171B5'
icol <- '#9ECAE0'
m.db <- subset(allmutants.db, total > 0)
d.db <- subset(allmutants.db, detected > 0)
m.db$mutations <- m.db$mtotal * 100.0 / m.db$total
d.db$detected <- d.db$mdetected * 100.0 / d.db$detected

@@

#grid.newpage()
#pushViewport(viewport(layout = grid.layout(1, 2)))
#print(p1, vp = vplayout(1, 1))
#print(p2, vp = vplayout(1, 2))
@
\caption{The relative contribution of mutation operators in terms of fraction of mutants produced and detected.}
\end{figure*}

\begin{figure*}
<<mutanttest,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
bcol <- '#2171B5'
icol <- '#9ECAE0'
m.db <- subset(allmutants.db, ncovering > 0)
d.db <- subset(allmutants.db, nkilling > 0)
m.db$covering <- m.db$tstcovering * 100.0 / m.db$ncovering
d.db$killing <- d.db$tstkilling * 100.0 / d.db$nkilling

tmp1 <- subset(m.db, select=c("mutator","covering"))
colnames(tmp1) <- c("mutator","tests")
tmp1$type <- "covering"

tmp2 <- subset(d.db, select=c("mutator","killing"))
colnames(tmp2) <- c("mutator","tests")
tmp2$type <- "killing"

tmp <- rbind(tmp1, tmp2)
tmp$type <- factor(tmp$type, levels=c("covering", "killing"))
tmp$mutator <- factor(tmp$mutator, levels=c("nmc", "rv", "ic", "dc", "nc", "rc", "vmc", "cc", "emv", "m", "cb", "i", "ri", "rs", "es", "in"))
options(warn=-1)
ggplot(aes(y=tests, x=mutator, fill=type),data=tmp) +
  geom_boxplot(outlier.color=NA, outlier.shape=NA) +
  scale_fill_manual(name = "Mutation Details", values = c(bcol, icol)
                    , labels = c("covering" = "Total covering", "killing" = "Total killing")) +
 theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
 theme(axis.line = element_line(colour = "black"))
options(warn=0)
@
\caption{The relative contribution of mutation operators in terms of fraction of tests killed and covered.}
\end{figure*}
